\TheTitle

### 2017-07-14 paper/design.tex
make use of "Merge-Tree" consistent

\begin{figure}[htpb]
  \centering
  \includegraphics[width=\linewidth]{figures/linvis/search_results.png}
  \caption{A single merge tree in the search results of \tool, showing
    the link to the root at the top and a table of the relevant commits
    in the bottom, sorted by relevance.}
  \label{fig:search_results}
\end{figure}

@@

The files tab shows an aggregated table of all files that were modified
in a merge. It includes metrics like the number of lines added, lines
removed, total lines modified, and the delta, summed across all commits
in the merge tree that modify this file. A details drop-down button
allows a user to see exactly which commit makes the changes, as shown in
Figure~\ref{fig:linvis_files}. If the current repository event being
viewed is a commit, the aggregate views will only show modifications
made by the commit.

The modules tab shows the modules modified in the merge tree. Like the
files tab, the modules tab uses a table to show the name of the module,
the number of commits that are in the merge tree that work with the
module, and a details button to provide the links to those commits.

@@

The list tree, depicted in Figure~\ref{fig:linvis_list_tree}, is
constructed as a series of nested lists. The nesting indicates the
parent-child relationship. This visualization is text-based enabling
fast navigation to commits using the built-in search in most
web-browsers. The list tree is rooted at the current repository event;
if the current event being inspected is a commit, only that commit will
be shown. Conversely, if the selected event is the root, the entire
merge tree will be shown.

>>>>

\begin{figure}[htpb]
  \centering
  \includegraphics[width=\linewidth]{figures/linvis/search_results.png}
  \caption{A single \mt tree in the search results of \tool, showing
    the link to the root at the top and a table of the relevant commits
    in the bottom, sorted by relevance.}
  \label{fig:search_results}
\end{figure}

@@

The files tab shows an aggregated table of all files that were modified
in a merge. It includes metrics like the number of lines added, lines
removed, total lines modified, and the delta, summed across all commits
in the \mt tree that modify this file. A details drop-down button
allows a user to see exactly which commit makes the changes, as shown in
Figure~\ref{fig:linvis_files}. If the current repository event being
viewed is a commit, the aggregate views will only show modifications
made by the commit.

The modules tab shows the modules modified in the \mt. Like the
files tab, the modules tab uses a table to show the name of the module,
the number of commits that are in the \mt tree that work with the
module, and a details button to provide the links to those commits.

@@

The list tree, depicted in Figure~\ref{fig:linvis_list_tree}, is
constructed as a series of nested lists. The nesting indicates the
parent-child relationship. This visualization is text-based enabling
fast navigation to commits using the built-in search in most
web-browsers. The list tree is rooted at the current repository event;
if the current event being inspected is a commit, only that commit will
be shown. Conversely, if the selected event is the root, the entire
\mt tree will be shown.

### 2017-07-14 paper/discussion.tex
make use of "Merge-Tree" consistent

% TODO: include info on merge tree sizes

@@

This algorithm relies heavily on the order of parents in the parent
list, but is able to trim the number of nodes that must be downloaded.
Furthermore, the resulting tree is able to show the order of commits,
telling the story of how a developer was working, before the set of
commits was merged. We developed a small Bitbucket plugin to test the
design and determine whether it was capable of producing merge trees,
shown in Figure~\ref{fig:b_plugin}.

>>>>

@@

This algorithm relies heavily on the order of parents in the parent
list, but is able to trim the number of nodes that must be downloaded.
Furthermore, the resulting tree is able to show the order of commits,
telling the story of how a developer was working, before the set of
commits was merged. We developed a small Bitbucket plugin to test the
design and determine whether it was capable of producing \mt{s},
shown in Figure~\ref{fig:b_plugin}.

### 2017-07-14 paper/introduction.tex
make use of "Merge-Tree" consistent

These methods and visualizations are implemented in a web-based tool
called \tool\footnote{\tool is currently available at
  \url{http://li.turingmachine.org}}. Our visualizations and tool
provide information about the location of any given commit or merge in
its respective merge-tree, the files edited, the modules edited, and the
commit message. \tool provides a search engine that filters commits by
commit hash, terms from the commit log, the author, filenames, and other
information. The results are then grouped together by the root of the
corresponding \mt.

>>>>

These methods and visualizations are implemented in a web-based tool
called \tool\footnote{\tool is currently available at
  \url{http://li.turingmachine.org}}. Our visualizations and tool
provide information about the location of any given commit or merge in
its respective \mt, the files edited, the modules edited, and the
commit message. \tool provides a search engine that filters commits by
commit hash, terms from the commit log, the author, filenames, and other
information. The results are then grouped together by the root of the
corresponding \mt.

### 2017-07-14 paper/model.tex
make use of "Merge-Tree" consistent

  \end{tikzpicture}
  \caption{Merge-tree view of the commits  represented in
    Figure~\ref{fig:repoEvents} showing the path they followed to reach
    the master branch. In this model the successors of each commit
    represents the path followed by that commit to reach the master
    branch.}
  \label{fig:repoTree}
\vspace{-3mm}
\end{figure}

@@

We used this information to evaluate the accuracy of the \mt model
extracted from the DAG\@. The method we followed started with the
extraction of the commit history up to July 20, 2016 form the Linux
repository. We computed the merge tree of every commit until that date.
Since Linus Torvalds mostly does merging directly into the master
branch, we assumed that every merge by Linus is the root of a \mt, later
detecting merges that do not merge into the master branch and removing
them from the set of root merges. As described above, the log of a
merge-commit usually contains the number of commits in the merge the
first 20 summaries of commits being merged. We extracted merges by Linus
Torvalds using the command \verb|git log --merges --author='Torvalds'|
and compared the number of commits according to the log with the number
of commits in the \mt rooted in this commit. We also used the summaries
of the commits found in the merge (not necessarily all---see above) to
make sure those commits were in their corresponding merge tree. For
example, for the merge in Figure~\ref{fig:sampleMerge} we would expect
that the merge tree rooted at \mycode{8cbd84f} contains 24 commits, and
the one-line summaries corresponds to commits in that \mt. We also
inspected those with differences to make sure they were true errors. The
results can be summarized as follows:

>>>>

  \end{tikzpicture}
  \caption{\mt view of the commits  represented in
    Figure~\ref{fig:repoEvents} showing the path they followed to reach
    the master branch. In this model the successors of each commit
    represents the path followed by that commit to reach the master
    branch.}
  \label{fig:repoTree}
\vspace{-3mm}
\end{figure}

@@

We used this information to evaluate the accuracy of the \mt model
extracted from the DAG\@. The method we followed started with the
extraction of the commit history up to July 20, 2016 form the Linux
repository. We computed the \mtof every commit until that date.
Since Linus Torvalds mostly does merging directly into the master
branch, we assumed that every merge by Linus is the root of a \mt, later
detecting merges that do not merge into the master branch and removing
them from the set of root merges. As described above, the log of a
merge-commit usually contains the number of commits in the merge the
first 20 summaries of commits being merged. We extracted merges by Linus
Torvalds using the command \verb|git log --merges --author='Torvalds'|
and compared the number of commits according to the log with the number
of commits in the \mt rooted in this commit. We also used the summaries
of the commits found in the merge (not necessarily all---see above) to
make sure those commits were in their corresponding \mt For
example, for the merge in Figure~\ref{fig:sampleMerge} we would expect
that the \mt rooted at \mycode{8cbd84f} contains 24 commits, and
the one-line summaries corresponds to commits in that \mt. We also
inspected those with differences to make sure they were true errors. The
results can be summarized as follows:

### 2017-07-14 paper/study.tex
make use of "Merge-Tree" consistent

\begin{table}[htpb]
  \centering
  \caption{Summarization Tasks}
  \label{tab:summarization_tasks}
  \begin{tabulary}{\linewidth}{LLL}
    \toprule
    Task Set   & Task & Description\\\midrule
    Merge      & T4   & What is the series of merges involved with merging this
    commit?\\
    & T5   & What other commits are merged?\\
    Authorship & T6   & How many authors are involved?\\
    & T7   & Who contributed the most changes?\\
    Files      & T8   & How many files were modified?\\
    & T9   & Which file had the most changes?\\
    Modules    & T10  & Which modules does this merge tree involve?\\
    \bottomrule
  \end{tabulary}
\end{table}

\textbf{The conceptual tasks} are designed to gain better insight on the
comprehension of the visualization in Gitk, and determine if it is
sufficient for understanding what other commits are related to a given
commit, and how those commits are merged. The tasks are outlined in
Table~\ref{tab:conceptual_tasks}. The tasks are performed in order using
Gitk. T1 has the participant draw a diagram of the merge tree,
which will be used to answer the other two questions. This enables us to
see issues with comprehending the DAG visualization. Participants are
given 10 minutes to perform this task, which also is used to familiarize
the participant with the Gitk interface, if they are not already, and
with the set of commits they will be working with. T2 and T3 are drawn
directly from the diagram from T1, giving quantitative metrics to
measure the comprehension. T2 asks the participant to verify the number
of commits, and T3 asks for the number of merges. The three tasks are
performed on both commits before continuing to the summarization tasks.

@@

While the merge task set is part of the summarization task group, it
focuses less with summarization of the commits and more with
comprehension of the model visualizations. The task is designed with two
goals in mind; first we want to measure and define which commits and
which merges the participant has defined to be in the merge tree; second
to help solidify which commits and merges will be used in the merge
tree.

@@

Statistical significance testing is performed to verify that the results
are meaningful. We use $alpha = 0.05$ or a $95\%$ confidence level. The
McNemar $\chi^2$ test\cite{McNemar1947} with continuity correct is used
to test the statistical significance of the hypothesis that \tool
improves correctness of the participants. The $\chi^2$ threshold
statistic at $\alpha = 0.05$ is 3.841. The Wilcoxon\cite{Wilcoxon45}
test and Cliff's effect size\cite{Cliff93} are applied to the accuracy
and timing metrics to determine the significance of the difference
between \tool and Gitk. The Wilcoxon test is applied between commits to
determine if the size of the merge-tree effects timing and accuracy. The
null hypotheses and alternative hypotheses are stated in
Table~\ref{tab:null_alt_hypoths}.

@@

We include two commits in the study to detect differences between \mt
sizes. The order that the commits are presented to each participant is
randomized. We analyzed the 15096 merge-trees from April 16th 2005 to
October 14th 2014, which corresponds to the releases Linux 2.6.12-rc3
and Linux 3.17-rc1. 25\% of the trees contain at most a single commit
not including the root, while 50\% of the trees contain at most seven
non-root nodes. 75\% of the trees contain at least 51 nodes, and the
largest tree contains 7217 nodes.

@@

\begin{figure}[bpt]
  \centering
  \begin{tabular}{ m{1.5cm} m{3cm} }
    \includegraphics[height=0.5in]{figures/commits/1-commit.pdf} &
    \includegraphics[height=1in]{figures/commits/7-commits.pdf}\\
  \end{tabular}
  \caption{The merge trees used in the user study,
    containing one and seven non-root nodes, respectively.}
  \label{fig:study_commits}
\end{figure}

@@

Table~\ref{tab:cross_commit_results} shows whether the merge-tree size
has an effect on the three studied metrics. An interesting observation
from the figure is that the correctness for T5 and T9 are effected by
the size of the merge-tree, but the accuracy is not. The correctness
results for T5 and T9 are shown in Figure~\ref{fig:correctness_t5_t9},
and the timing results for T7 are shown in Figure~\ref{fig:timing_t7}.

@@

    While there is a difference in correctness between different-sized
    merge-trees, \tool improves correctness of determining the other
    commits related to a commit in trees of varying sizes. The
    difference in the two commits stem from the participants that did
    not change outcomes between the tools.

>>>>

\begin{table}[htpb]
  \centering
  \caption{Summarization Tasks}
  \label{tab:summarization_tasks}
  \begin{tabulary}{\linewidth}{LLL}
    \toprule
    Task Set   & Task & Description\\\midrule
    Merge      & T4   & What is the series of merges involved with merging this
    commit?\\
    & T5   & What other commits are merged?\\
    Authorship & T6   & How many authors are involved?\\
    & T7   & Who contributed the most changes?\\
    Files      & T8   & How many files were modified?\\
    & T9   & Which file had the most changes?\\
    Modules    & T10  & Which modules does this \mt involve?\\
    \bottomrule
  \end{tabulary}
\end{table}

\textbf{The conceptual tasks} are designed to gain better insight on the
comprehension of the visualization in Gitk, and determine if it is
sufficient for understanding what other commits are related to a given
commit, and how those commits are merged. The tasks are outlined in
Table~\ref{tab:conceptual_tasks}. The tasks are performed in order using
Gitk. T1 has the participant draw a diagram of the \mt,
which will be used to answer the other two questions. This enables us to
see issues with comprehending the DAG visualization. Participants are
given 10 minutes to perform this task, which also is used to familiarize
the participant with the Gitk interface, if they are not already, and
with the set of commits they will be working with. T2 and T3 are drawn
directly from the diagram from T1, giving quantitative metrics to
measure the comprehension. T2 asks the participant to verify the number
of commits, and T3 asks for the number of merges. The three tasks are
performed on both commits before continuing to the summarization tasks.

@@

While the merge task set is part of the summarization task group, it
focuses less with summarization of the commits and more with
comprehension of the model visualizations. The task is designed with two
goals in mind; first we want to measure and define which commits and
which merges the participant has defined to be in the \mt; second
to help solidify which commits and merges will be used in the merge
tree.

@@

Statistical significance testing is performed to verify that the results
are meaningful. We use $alpha = 0.05$ or a $95\%$ confidence level. The
McNemar $\chi^2$ test\cite{McNemar1947} with continuity correct is used
to test the statistical significance of the hypothesis that \tool
improves correctness of the participants. The $\chi^2$ threshold
statistic at $\alpha = 0.05$ is 3.841. The Wilcoxon\cite{Wilcoxon45}
test and Cliff's effect size\cite{Cliff93} are applied to the accuracy
and timing metrics to determine the significance of the difference
between \tool and Gitk. The Wilcoxon test is applied between commits to
determine if the size of the \mt effects timing and accuracy. The
null hypotheses and alternative hypotheses are stated in
Table~\ref{tab:null_alt_hypoths}.

@@

We include two commits in the study to detect differences between \mt
sizes. The order that the commits are presented to each participant is
randomized. We analyzed the 15096 \mt{s} from April 16th 2005 to
October 14th 2014, which corresponds to the releases Linux 2.6.12-rc3
and Linux 3.17-rc1. 25\% of the trees contain at most a single commit
not including the root, while 50\% of the trees contain at most seven
non-root nodes. 75\% of the trees contain at least 51 nodes, and the
largest tree contains 7217 nodes.

@@

\begin{figure}[bpt]
  \centering
  \begin{tabular}{ m{1.5cm} m{3cm} }
    \includegraphics[height=0.5in]{figures/commits/1-commit.pdf} &
    \includegraphics[height=1in]{figures/commits/7-commits.pdf}\\
  \end{tabular}
  \caption{The \mt{s} used in the user study,
    containing one and seven non-root nodes, respectively.}
  \label{fig:study_commits}
\end{figure}

@@

Table~\ref{tab:cross_commit_results} shows whether the \mtsize
has an effect on the three studied metrics. An interesting observation
from the figure is that the correctness for T5 and T9 are effected by
the size of the \mt, but the accuracy is not. The correctness
results for T5 and T9 are shown in Figure~\ref{fig:correctness_t5_t9},
and the timing results for T7 are shown in Figure~\ref{fig:timing_t7}.

@@

    While there is a difference in correctness between different-sized
    \mt{s}, \tool improves correctness of determining the other
    commits related to a commit in trees of varying sizes. The
    difference in the two commits stem from the participants that did
    not change outcomes between the tools.
